Simulation Comparison

### 2020-12-02 output_scripts/cmmhp_comparison/sim_comparison.Rmd
check the sparse models also

dc_sim_path <- here::here("output", "sims", "sims_m3_dc")
comm_sim_path <- here::here("output", "common_rate", "sims_m3")
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')

@@

```{r ks-pr-computation-dc}
object_par <- list(sim_lambda_0 = 0.08,
                   sim_lambda_1 = 0.16,
                   sim_eta_1 = 2.5,
                   gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
                   zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1 = c(0.1, 0.2, 0.4, 0.7, 0.9))

## Iteration on 50 simulations
for(s in c(1:n_sim)){
  load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
  load(here(dc_sim_path,paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

@@

```{r ks-pr-common-rate model}
complete_sims <- 1:n_sim
complete_sims <- complete_sims[-29]

@@

## Iteration on 50 simulations
for(s in 30:n_sim){
  load(here(comm_sim_path, paste0("sim_model3_fit123_",s,".RData")))
  load(here(comm_sim_path, paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

>>>>

dc_sim_path <- here::here("output", "sims_m3_sparse")
comm_sim_path <- here::here("output", "common_rate", "sims_m3")
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')

@@

```{r ks-pr-computation-dc}
object_par <- list(sim_lambda_0 = 0.08,
                   sim_lambda_1 = 0.16,
                   sim_eta_1 = 2.5,
                   gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
                   zeta_var = c(0.075, 0.06, 0.05, 0.03, 0.02),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1 = c(0.1, 0.2, 0.4, 0.7, 0.9))

N_array <- array(0, dim = c(n_sim, length(object_par$f_vec_1),
                         length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1)))
Lambda_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1))) 
PR_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1))) 
PR_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1))) 
KS_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1)))
KS_p_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_p_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
current_sims <- 1:n_sim
# 7,31,34,43,47,49
## Iteration on 50 simulations
for(s in 44:n_sim){
  load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
  load(here(dc_sim_path,paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

@@

```{r ks-pr-common-rate model}
complete_sims <- 1:n_sim
#complete_sims <- complete_sims[-29]

@@

## Iteration on 50 simulations
for(s in 1:n_sim){
  load(here(comm_sim_path, paste0("sim_model3_fit123_",s,".RData")))
  load(here(comm_sim_path, paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))
